\maketitle  % command to print the title page with above variables
\setcounter{page}{1}
%---------------------------------------------------------------------
%                  영문 초록을 입력하시오
%---------------------------------------------------------------------
\begin{abstracts}     %this creates the heading for the abstract page
	\addcontentsline{toc}{section}{Abstract}  %%% TOC에 표시
	\noindent{
This study developed GS-system (Gyeonggi Science highschool for the gifted-system) for the automation of small astronomical telescopes. As astronomical telescopes become popular now, the automation process of small telescopes is drawing attention. Thus, by developing and controlling a tube cover to control the Bahtinov mask, various convenient functions needed for the automation of the astronomical observation were provided. GS-system is divided into drive part and control part. The drive part consists the control of the cover and hardware for convenience functions such as hot-wire control, power control, and motor control. The control part improves the existing motor focuser and ASCOM compatible driver to allow control of newly controlled parts using the existing ASCOM-enabled software. GS-system is believed to be of great help to the astronomical observation of small telescopes in the future.
	
		key word : Telescope, Automation, Teensy
	}
\end{abstracts}

\begin{abstractskor}
본 연구에서는 소형 천체망원경의 자동화를 위한 GS-system (Gyeonggi Science highschool for the gifted-system) 을 개발하였다. 현재 천체망원경이 대중화됨에 따라 소형 천체망원경의 자동화 과정이 주목을 받고 있다. 이에 바흐티노프 마스크를 제어할 수 있는 경통의 덮개를 개발하여 이를 제어함으로써 천체관측의 자동화에 필요한 여러 가지 편의기능들을 제공할 수 있도록 하였다. GS-system은 구동부와 제어부로 나뉜다. 구동부에서는 경통의 덮개 및 열선 제어, 전원 제어, 초점 제어 등의 편의기능들을 위한 하드웨어들로 구성되어 있다. 제어부는 기존의 모터포커서 및 ASCOM 호환 드라이버를 개선하여 구동부를 제어할 수 있도록 하였다. GS-system은 앞으로의 소형 천체망원경의 천체관측에 많은 도움이 될 수 있을 것으로 사료된다.

키워드 : 자동망원경, 자동화, Teensy
	
\end{abstractskor}
%----------------------------------------------
%   Table of Contents (자동 작성됨)
%----------------------------------------------
\cleardoublepage
\addcontentsline{toc}{section}{Contents}
\setcounter{secnumdepth}{3} % organisational level that receives a numbers
\setcounter{tocdepth}{3}    % print table of contents for level 3
\baselineskip=2.2em
\tableofcontents


%----------------------------------------------
%     List of Figures/Tables (자동 작성됨)
%----------------------------------------------
\cleardoublepage
\clearpage
\listoffigures	% 그림 목록과 캡션을 출력한다. 만약 논문에 그림이 없다면 이 줄의 맨 앞에 %기호를 넣어서 코멘트 처리한다.

\cleardoublepage
\clearpage
\listoftables  % 표 목록과 캡션을 출력한다. 만약 논문에 표가 없다면 이 줄의 맨 앞에 %기호를 넣어서 코멘트 처리한다.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Main Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cleardoublepage
\clearpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}



